%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Academic Projects}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
%---------------------------------------------------------
  \cventry
    {cse343 - machine learning} % Job title
    {ML{\hspace{0.2em}\cdotp\hspace{0.2em}}DL | Classifying Driving Behaviour} % Organization
    {} % Location
    {} % Date(s)
    {
      \begin{cvitems}
        \item {Idea : Classifying driving behaviour as normal, aggressive and drowsy using dash-cam videos.}
        \item {Trained and tested on \href{http://www.robesafe.uah.es/personal/eduardo.romera/uah-driveset/}{UAH-DriveSet dataset}.}
        \item {Implemented 3 DL models and 1 ML model with Conv-LSTM outperforming others with 92\% accuracy.}
      \end{cvitems}
    }
%     \parbox[position][height][inner-pos]{width}{text}
    {\multirow{2}{1.1cm}{\parbox{1\linewidth}{\vspace{0.1cm}}}}

%---------------------------------------------------------
  \cventry
    {cse535 - mobile computing} % Job title
    {Android App | Draw on Video Call} % Organization
    {} % Location
    {} % Date(s)
    {
      \begin{cvitems}
        \item {Idea : Live drawing over the video frames that are visible to both parties over a video call.}
        \item {Helped in ideation of how live drawing will be implemented using firebase.}
        \item {Implemented color palette, brush layout, multiple color support and smooth animation of publisher-subscriber containers switching.}
      \end{cvitems}
    }
%     \parbox[position][height][inner-pos]{width}{text}
    {\multirow{2}{1.1cm}{\parbox{1\linewidth}{\vspace{0.1cm}}}}

%---------------------------------------------------------
  \cventry
    {cse231 - operating systems} % Job title
    {xv6 | Swapping{\hspace{0.2em}\cdotp\hspace{0.2em}}Demand Paging} % Organization
    {} % Location
    {} % Date(s)
    {
      \begin{cvitems}
        \item {Implemented Swapping : When OS runs out of RAM, swap out pages to disk to reuse them.}
        \item {Implemented Demand Paging : Lazily mapping physical page corresponding to a virtual page when it is dereferenced. Get a new physical page, map it and restore the content from disk if it was swapped earlier.}
      \end{cvitems}
    }
%     \parbox[position][height][inner-pos]{width}{text}
    {\multirow{2}{1.1cm}{\parbox{1\linewidth}{\vspace{0.1cm}}}}

%---------------------------------------------------------
  \cventry
    {cse201a - advanced programming} % Job title
    {Superstore Management Desktop App} % Organization
    {} % Location
    {} % Date(s)
    {
      \begin{cvitems}
        \item {Designed and developed a Java based management system for a Superstore using JavaFX and Scene Builder.}
        \item {Application model designed using UML diagrams following the Object Oriented Design concepts.}
        \item {Developed the server-client architecture using sockets and threads.}
        \item {Implemented a database in Java and designed the FXML visual layouts using Scene Builder.}
      \end{cvitems}
    }
%     \parbox[position][height][inner-pos]{width}{text}
    {\multirow{2}{1.1cm}{\parbox{1\linewidth}{\vspace{0.1cm}}}}

%---------------------------------------------------------

\end{cventries}